---
title: "ETC513 Assignment 4: Practical Driving Tests in Queensland"
author:
- familyname: Chen
  othernames: Shaohu
  address: Monash Universtidy
  email: sche0232@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics(In Progress)
- familyname: Duan
  othernames: Qian
  address: Monash Universtidy
  email: qdua0005@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics(In Progress)
- familyname: Tsou
  othernames: Tina
  address: Monash Universtidy
  email: ttso0004@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics(In Progress)
department: Practical Driving Examination Board
organization: Queensland Government
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE,echo = FALSE, message = FALSE, warning = FALSE,fig.align='center'}
# Libraries
library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
library(ggplot2)
drive <- read_csv(here::here("Data/practicaldrivingexaminationresults.csv"))
```

\section*{Introduction}

**Data Description:**

This data set is [Practical driving examination results for customers](https://data.gov.au/dataset/ds-qld-3f90a4c3-23df-49dc-b243-9a29c0b23dd5/details?q=Practical%20driving) which is provided by local government authority (LGA) of Queensland. It records the license class, booking type, examination results and driver age group during 2005 to 2019.

**Research aims:**

We divided into three parts, the first part focuses on the annual pass rate of different local government authority. 

The second part mainly aims to compare the age group with different license. 

The third part calculates the correlation between the examination results and booking type.

Using @R, we ran analysis to explore our research goals. This analysis uses R packages @tidyverse, @readr, @kableExtra, @bookdown, @ggplot2, @fastDummies, @scales, @stargazer, @broom, and @pROC.

\section*{Part 1}

The first part focuses on the annual pass rate of different local government authority. 

```{r,echo = FALSE, message = FALSE}
year_drive <- drive %>% 
 separate(col = Month, into = c("Year","Month"),"-") %>% 
  select(Year,`Local Government Authority`)  
num_year_drive <- year_drive %>% count(Year)

num_year_drive_percentage <- drive %>% 
  separate(col = Month, into = c("Year","Month"),"-") %>% 
  select(Year,Month,`Local Government Authority`,`Exam Result`) %>% 
  count(Year,`Exam Result`) %>% 
  arrange(desc(Year)) %>% 
  rename(num = n) %>% 
  right_join(num_year_drive) %>% 
  mutate(year_percentage = num/n) %>% 
  filter(`Exam Result` == 'PASS') %>% 
  rename(pass_num = num, total_num = n) %>% 
  select(Year,year_percentage)
```


```{r,echo = FALSE, message = FALSE}
num_drive <- year_drive %>% 
  count(Year,`Local Government Authority`) %>% 
  arrange(desc(Year)) 

percentage_num_drive <- drive %>% 
 separate(col = Month, into = c("Year","Month"),"-") %>% 
  select(Year,Month,`Local Government Authority`,`Exam Result`) %>% 
  count(Year,`Local Government Authority`,`Exam Result`) %>% 
  arrange(desc(Year)) %>% 
  rename(num = n) %>% 
  right_join(num_drive)  %>% 
  mutate(percentage = num/n)%>% 
  filter(`Exam Result` == 'PASS') %>% 
  rename(pass_num = num, total_num = n)%>% 
  left_join(num_year_drive_percentage)

num_dict <- percentage_num_drive %>% count(Year) %>% rename(total_num = n)
```


```{r Fig1, message = FALSE, warning= FALSE, echo=FALSE, fig.height= 7, fig.width=15,fig.cap="Year Pass Percentage(year_percentage) and Percentage of Local Government Authority annual passing rates exceeding the total annual passing rate(num_percentage)"}
over_percentage <- percentage_num_drive %>% 
  filter(percentage > year_percentage) %>% 
  count(Year,year_percentage) %>% 
  left_join(num_dict) %>% 
  mutate(num_percentage = n / total_num) %>% 
  select(-n,-total_num) 

over_percentage_longer <-over_percentage %>% 
  pivot_longer(cols = year_percentage:num_percentage,
               names_to = "percentage",
               values_to = "vlues")

ggplot(over_percentage_longer) +
  geom_line(aes(x= as.numeric(Year),
                y = vlues*100,
                colour = percentage,
                group = percentage))+
  xlab("Year")+
  ylab("Percentage")+
  ggtitle("Year Pass Percentage and Number Percentage per year ")+
scale_y_continuous(labels = scales::percent_format(scale = 1))+
   theme_minimal() 

```

In the figure \@ref(fig:Fig1), as for the annual pass rate, it does not fluctuate greatly, and basically remained at 62.5% but the percentage of the number exceeding the annual pass rate fluctuates greatly, which may be due to missing data in some regions, however, from the data point of view, it has been in an upward phase in recent years.

```{r Tab1, message = FALSE, warning= FALSE, echo=FALSE,fig.width= 15}
count_function <- function(x){percentage_num_drive %>% 
  select(Year,`Local Government Authority`,percentage) %>% 
  group_by(Year) %>% 
  filter(percentage == x(percentage)) %>% 
  group_by(`Local Government Authority`) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))}

max_percetage <- count_function(max) %>% head(6)
min_percetage <- count_function(min) %>% head(6)

knitr::kable(max_percetage,
             caption = "Number of time getteing the highest pass rate per year",
             booktabs = TRUE) %>%
   kable_styling(bootstrap_options  = c("striped", "hold_position")) 

```

```{r Tab2, message = FALSE, warning= FALSE, echo=FALSE,fig.width= 15,}
knitr::kable(min_percetage,
             caption = "Number of time getteing the lowest pass rate per year",
             booktabs = TRUE) %>%
   kable_styling(bootstrap_options  = c("striped", "hold_position"))
```

In the table \@ref(tab:Tab1), BLACKALL-TAMBO REGIONAL COUNCIL has the most number of first (`r max_percetage$count[1]` times). In the table \@ref(tab:Tab2), MAREEBA SHIRE COUNCIL, NAPRANUM ABORIGINAL SHIRE COUNCIL, REDLAND CITY COUNCIL have won the last `r min_percetage$count[1]` times.

```{r,echo = FALSE, message = FALSE}
max_min_percentage2 <- percentage_num_drive %>% 
  filter(`Local Government Authority` %in% c("BLACKALL-TAMBO REGIONAL COUNCIL",
                                             "MAREEBA SHIRE COUNCIL",
                                             "REDLAND CITY COUNCIL")) 
```

```{r Fig2, fig.height= 7, fig.width=15, echo=FALSE,message = FALSE, warning= FALSE, echo=FALSE,fig.cap="Year Pass Percentage in BLACKALL-TAMBO REGIONAL COUNCIL, BLACKALL-TAMBO REGIONAL COUNCIL, and REDLAND CITY COUNCIL"}
ggplot()+
  geom_line(max_min_percentage2,mapping = aes(x= as.numeric(Year),
                y = percentage*100,
                group = `Local Government Authority`,
                colour = `Local Government Authority`))+
  geom_line(over_percentage,mapping = aes(x = as.numeric(Year), y = year_percentage*100), 
            size = 1, color = "gold")+
  scale_y_continuous(name = "Year Pass Percentage",labels = scales::percent_format(scale = 1))+ 
  xlab("Year") +
  ggtitle("Year Pass Percentage per year")+
   theme_minimal()

```

According to the figure \@ref(fig:Fig2), the annual pass rate of BLACKALL-TAMBO REGIONAL COUNCIL has been on the rise after 2007, even reaching 100%, while the annual pass rate of MAREEBA SHIRE COUNCIL is in a downward state, and the annual pass rate of REDLAND CITY COUNCIL basically fluctuates at 55%. Especially, MAREEBA SHIRE COUNCIL and REDLAND CITY COUNCIL have been lower than the annual pass rate since 2015, which the gold line is year pass rate.

```{r Fig3, fig.height=7, fig.width=15,fig.cap="Year Pass Number in BLACKALL-TAMBO REGIONAL COUNCIL, MAREEBA SHIRE COUNCIL, and REDLAND CITY COUNCIL",echo = FALSE, message = FALSE}
ggplot()+
  geom_line(max_min_percentage2,mapping = aes(x= as.numeric(Year),
                y = pass_num,
                group = `Local Government Authority`,
                colour = `Local Government Authority`))+ 
  ylab("Number of Pass")+
  xlab("Year") +
  ggtitle("Year Pass Number per year")+
   theme_minimal() 
```

In the figure \@ref(fig:Fig3), the number of pass for three government authorities basically has little fluctuation. Interestingly, the ranking of the number of passes and the ranking of the pass rate are completely opposite. 

Therefore, the annual pass rate has not changed much, the percentage of the number exceeding the annual pass rate fluctuates greatly. Areas with sparsely populated areas may have fewer people participating, resulting in a higher overall pass rate than areas with densely populated areas.


\section*{Part 2}
```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = TRUE, message = FALSE, warning = FALSE)
library(scales)
```

```{r}
### The whole pass rate of Queensland
wholerate <- drive %>%
  group_by(`Exam Result`) %>%
  count() %>%
  pivot_wider(id_cols = `Exam Result`,
              names_from = `Exam Result`,
              values_from = n) %>%
  mutate(passrate = PASS/(FAIL+PASS))
```

The driving examination pass rate of Queensland is `r head(percent(wholerate$passrate))` .

```{r passrate}
#count the pass rate of each product type
type <- drive %>%
  group_by(`Product Type Name`, `Exam Result`) %>%
  count() %>%
  pivot_wider(id_cols = -`Exam Result`,
              names_from = `Exam Result`,
              values_from = n) %>%
  mutate(sum = FAIL + PASS,
         pass_rate = round(PASS /sum,2))%>%
  select(`Product Type Name`, pass_rate) %>%
  arrange(pass_rate) %>%
  mutate(pass_rate = percent(pass_rate))

knitr::kable(type, caption = "The pass rate of each product type",
             booktabs = TRUE) %>%
   kable_styling(latex_options = c("striped", "hold_position"))
```

+ The table \@ref(tab:passrate) is the pass rate of different licenses. Above all, the automatic car has the lowest passing rate with 53%, Since the car has the largest amount of popularity to meet people daily command, so there are more people to join the test of cars. 

+ While the motorcycle over 250cc has the largest pass rate with 86%. The motorcycle is much more professional, and it required people got the license up to 250cc who can take part in the test. Therefore, these people are professional so got a higher rate.

```{r failrate, fig.align='center', warnings = FALSE, fig.cap="Queensland driving test fail rates by age"}
fail <- drive %>%
 separate(col = Month,
          into = c("year",
                   "month"),
          "-") %>%
  mutate(year = as.numeric(year)) %>%
  filter(year %in% c("2005" : "2019" ))%>%
  group_by(`Driver Age Group`, `Exam Result`) %>%
  count() %>%
  pivot_wider(id_cols = -`Exam Result`,
              names_from = `Exam Result`,
              values_from = n) %>%
  mutate(sum = FAIL + PASS,
         fail_rate = round(FAIL /sum * 100, 3)) %>%
  mutate(Age_group1 = str_remove(`Driver Age Group`, "Aged"),
         Age_group2 = str_remove(Age_group1, "years")) %>%
  rename(age_group = Age_group2) %>%
  select(age_group, fail_rate) 

# plot the fail rate 
ggplot(fail,
       aes(x = age_group,
           y = fail_rate,
           group = 1))+
  geom_line(color = "#8FBC94", size = 1)+
  geom_point(color = "#548687", size = 2)+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90))

```

Figure \@ref(fig:failrate), describes the failing rate of different age groups. It can be seen that the fail rate is increasing with the age grows older. Because people is 81 years old and over has the highest fail rate, which means it is hard for people to pass the driving license after 61 years old. However, there is one interesting point for young people with high rate at 41%. Basically, the people in this range takes the highest number of examinations. While in the original data set, some young people around these ages have 200- or 300-times test, but still failed. Australia government has more restrictions on young people driving license, so the rate is high.


```{r}
# select the age group
age <- drive %>%
  select(`Product Type Name`, `Driver Age Group`, `Exam Result`, `Number of Examinations`) %>%
  mutate(Age_group1 = str_remove(`Driver Age Group`, "Aged"),
         Age_group2 = str_remove(Age_group1, "years"),
         licence = str_remove(`Product Type Name`, "CLASS")) %>%
  rename(age_group = Age_group2) %>%
# count the pass rate by different product type
  group_by(licence, age_group, `Exam Result`) %>%
  count()
```


```{r license, fig.cap="Compare the fail and pass in different license"}
# plot the age group by license
ggplot(age,
       aes(x = age_group,
           y = n,
           fill = `Exam Result`))+
  geom_bar(stat = "identity", position = "fill", width=2)+
  geom_hline(yintercept = 0.5, color = "black")+
  facet_wrap(~licence, scales = "free_x", nrow = 2)+
  scale_fill_manual(values=c("#6E7783", "#77AAAD"))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90))
 
```

In Figure \@ref(fig:license), for most drive license, the number of pass all exceeds 50% of all age, except the automatic car license. People who fails at an older age. The number of fails is much more than pass. 
Another interesting point is that in motorcycle and heavy vehicle, people over 70 years old get 100% pass rate. This is mainly because there are only one or two people join the test and he pass. So, the pass rate is 100%. This doesn’t mean all old people can get the license for one time.

\section*{Part 3}


