---
title: "ETC513 Assignment 3: Comparison of Energy and Pollution by Country"
author:
- familyname: Chen
  othernames: Shaohu
  address: Monash Universtidy
  email: sche0232@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics(In Progress)
- familyname: Duan
  othernames: Qian
  address: Monash Universtidy
  email: qdua0005@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics(In Progress)
- familyname: Tsou
  othernames: Tina
  address: Monash Universtidy
  email: ttso0004@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics(In Progress)
department: Our consultancy \newline add names &\newline add names
organization: Australian Government 
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
# editor_options: 
#   chunk_output_type: console
---

```{r ,echo = FALSE, message = FALSE, warning = FALSE}
# Libraries
library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
library(fastDummies)
library(scales)
library(broom)
drive <- read_csv("Data/practicaldrivingexaminationresults.csv")
```

\section*{Introduction}




\section*{Step 1}




\section*{Step 2}


\section*{Step 3}

```{r}
drivedum <- dummy_cols(drive, select_columns =  c('Booking Type', 'Exam Result', 'Product Type Name'),
                       remove_selected_columns = TRUE)
train <- drivedum[1:252813,]
test <- drivedum[252814:337084,]

logmodel <- glm(`Exam Result_PASS` ~`Booking Type_Private`, family=binomial(link='logit'),data=train)

summary(logmodel)
anova(logmodel, test="Chisq")
```

```{r accuracy}
fitted.results <- predict(logmodel,newdata=test,type='response')
fitted.results <- ifelse(fitted.results > 0.5,1,0)
misClasificError <- mean(fitted.results != test$`Exam Result_PASS`)
print(paste('Accuracy',1-misClasificError))
```
// end of logistic regression model testing

```{r frequency table}
table <- table(drive$`Booking Type`,drive$`Exam Result`)
addmargins(table)
tab.prop <-  prop.table(table, 1)
```
A quick look at the frequency table between *Booking Type* and *Exam Result* and we saw that the number of people who passed the exam is similar for both driving school and private.

```{r chisq.test}
chisq.test(drive$`Booking Type`,drive$`Exam Result`)
```
However, when we run a chi-square test, the p-value is 0.0121 so we have statistical evidence that there is a relationship between *Booking Type* and *Exam Result*.

```{r}
tab.df <- as.data.frame(tab.prop)#make frequency table into data frame
names(tab.df) <- c("Booking Type", "Result", "frequency")

ggplot(tab.df, 
       aes(x=`Booking Type`, y = frequency, fill=Result)) + 
        geom_col() +theme_minimal()
```

```{r plot_bookingtype_model}
plot_df <- augment(logmodel, type.predict = "response")

base <-
  ggplot(plot_df, aes(x = `Booking Type_Private`)) +
  geom_line(aes(y = .fitted), color = "blue") +
  labs(x = "Booking Type", y = "Pass")

base + geom_point(aes(y = `Exam Result_PASS`), alpha = 0.2)
```


